\cvsection{Work Experience}
\begin{cventries}

  \cventry
  {Winter Intern, Neonatology Dept., Team Member}
  {{Government Medical College \& Hospital}}
  {Aurangabad, India}
  {Dec'18 - Jan'19}
  {
    \begin{cvitems}
    \vspace{1mm}
    \justifying{
        \item Worked on a scalable web application with an extensive technology stack using Django \& MySQL.
        \item Solved the problem of an outdated way of storage, maintenance \& analysis of patient’s records from registers.
        \item Presented a web-based platform to assist doctors with the filling up of the follow-up forms as well as storing the classified patient data securely on the server.
        \item Provided graphs \& visualization to help the doctors with analysis \& interpretation of the trends among the patients.
        \item Used Git Version Control tool to coordinate team-development.
     }  
   \end{cvitems}
  }
  
  \cventry
  {Software Engineering, Virtual Internship {\href{https://insidesherpa.s3.amazonaws.com/completion-certificates/JP\%20Morgan/R5iK7HMxJGBgaSbvk_JPMorgan\%20Chase_nvRBxnrAcvA4EvS4y_completion_certificate.pdf}{\scriptsize\faLink}}}
  {{JP Morgan Chase \& Co.}}
  {India}
  {June 2020}
  {
    \begin{cvitems}
    \vspace{1mm}
    \justifying{
        \item Worked on Perspective framework provided by J.P. Morgan for data analysis.
        \item Established financial data-feeds in Real Time Stock Prize analysis.
        \item Built Visualization Graphs of stock price using React.
     }  
   \end{cvitems}
  }
  
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv.tex"
%%% End: